DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-27 ase2017/paper.tex
typo

Recently, a new methodology to synthesize digital control systems was proposed, 
named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine that is able to produce digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. Program synthesis engines 
use a specification as the starting point, and subsequently produce a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines as the one used here combine automated testing, genetic algorithms 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
DSSynth synthesizes stable digtal controllers using that CEGIS-based approach,
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

>>>>

Recently, a new methodology to synthesize digital control systems was proposed, 
named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine that is able to produce digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. Program synthesis engines 
use a specification as the starting point, and subsequently produce a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines as the one used here combine automated testing, genetic algorithms 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
DSSynth synthesizes stable digital controllers using that CEGIS-based approach,
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.
